Review of Polymer Solutions for Near-Field Electrospinning with Spatial Control

### 2019-06-17 NFES_Review/article.tex
art progress (table complete?)

@@

 &
   &
   &
  \textbf{Solution Concentration: } \mbox{}\protect\newline \textbf{Nozzle:} \mbox{}\protect\newline \textbf{Solution deposition rate: } \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: } \mbox{}\protect\newline \textbf{Substrate composition: } \mbox{}\protect\newline \textbf{Applied voltage:} \mbox{}\protect\newline \textbf{x-y stage velocity:} \mbox{}\protect\newline \textbf{Fiber Diameter: } \mbox{}\protect\newline \textbf{Distance between adjacent fibers: } &
  \\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 &
   &
   &
  \textbf{Solution Concentration: } \mbox{}\protect\newline \textbf{Nozzle:} \mbox{}\protect\newline \textbf{Solution deposition rate: } \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: } \mbox{}\protect\newline \textbf{Substrate composition: } \mbox{}\protect\newline \textbf{Applied voltage:} \mbox{}\protect\newline \textbf{x-y stage velocity:} \mbox{}\protect\newline \textbf{Fiber Diameter: } \mbox{}\protect\newline \textbf{Distance between adjacent fibers: } &
  \\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 &
   &
   &
  \textbf{Solution Concentration: } \mbox{}\protect\newline \textbf{Nozzle:} \mbox{}\protect\newline \textbf{Solution deposition rate: } \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: } \mbox{}\protect\newline \textbf{Substrate composition: } \mbox{}\protect\newline \textbf{Applied voltage:} \mbox{}\protect\newline \textbf{x-y stage velocity:} \mbox{}\protect\newline \textbf{Fiber Diameter: } \mbox{}\protect\newline \textbf{Distance between adjacent fibers: } &
  \\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 &
   &
   &
  \textbf{Solution Concentration: } \mbox{}\protect\newline \textbf{Nozzle:} \mbox{}\protect\newline \textbf{Solution deposition rate: } \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: } \mbox{}\protect\newline \textbf{Substrate composition: } \mbox{}\protect\newline \textbf{Applied voltage:} \mbox{}\protect\newline \textbf{x-y stage velocity:} \mbox{}\protect\newline \textbf{Fiber Diameter: } \mbox{}\protect\newline \textbf{Distance between adjacent fibers: } &
  \\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 &
   &
   &
  \textbf{Solution Concentration: } \mbox{}\protect\newline \textbf{Nozzle:} \mbox{}\protect\newline \textbf{Solution deposition rate: } \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: } \mbox{}\protect\newline \textbf{Substrate composition: } \mbox{}\protect\newline \textbf{Applied voltage:} \mbox{}\protect\newline \textbf{x-y stage velocity:} \mbox{}\protect\newline \textbf{Fiber Diameter: } \mbox{}\protect\newline \textbf{Distance between adjacent fibers: } &
  \\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
 &
   &
   &
  \textbf{Solution Concentration: } \mbox{}\protect\newline \textbf{Nozzle:} \mbox{}\protect\newline \textbf{Solution deposition rate: } \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: } \mbox{}\protect\newline \textbf{Substrate composition: } \mbox{}\protect\newline \textbf{Applied voltage:} \mbox{}\protect\newline \textbf{x-y stage velocity:} \mbox{}\protect\newline \textbf{Fiber Diameter: } \mbox{}\protect\newline \textbf{Distance between adjacent fibers: } &
  \\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}

@@

>>>>

  Typical NFES process &

@@

Poly(9-Vinyl Carbazole) (PVK) &
  Styrene &
  Typical NFES process &
  \textbf{Solution Concentration:} 3.96$wt\% $ PVK in styrene \mbox{}\protect\newline \textbf{Nozzle:} Needle inner diameter of 100$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 500$nL/min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} around 2.5$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Si/SiO2 \mbox{}\protect\newline \textbf{Applied voltage:} 3-4$kV $ \mbox{}\protect\newline x-y stage velocity: 13.3$cm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 289.26 $\pm $ 35.37$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers: }50$\mu m $ \mbox{}\protect\newline \textbf{Notes:} 15$m $ yield in 2$min $ &
  \unskip~\cite{527120:11974316}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
Polystyrene (PS) &
  1,2,4-Trichloro benzene &
  Electrohydro-dynamic (EHD) jet printing &
  \textbf{Solution Concentration:} 1 to 5$wt\% $ PS \mbox{}\protect\newline \textbf{Nozzle:} Glass nozzle inner diameter of 2$\mu m $ and outer diameter of 2.66$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} Si \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance: 20, 30, 40$\mu m $} \mbox{}\protect\newline \textbf{Substrate composition: } \mbox{}\protect\newline \textbf{Applied voltage:} 500 to 400$V $ in 25$V $ increments \mbox{}\protect\newline \textbf{x-y stage velocity:} 0.01-10$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} about 60-170$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
  \unskip~\cite{527120:11974320}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
  Typical NFES process &
  \textbf{Solution Concentration:} 3$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:}\textit{Not determined} \mbox{}\protect\newline \textbf{Solution deposition rate:} \textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 500$\mu m $ \mbox{}\protect\newline \textbf{Substrate composition:} Si \mbox{}\protect\newline \textbf{Applied voltage:} 1000$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$cm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 300$nm $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 25$\mu m $ &
  \unskip~\cite{527120:11974321}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
  Multinozzle NFES &
  \textbf{Solution Concentration:} 5$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} four-nozzle and six-nozzle array with needle spacing changes from 1.5$mm $ to 3.5$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 1-3$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition:}\textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 1.7-2.7$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} 5.47$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 3-5 $mm $ &
  \unskip~\cite{527120:11974322}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
  Multinozzle NFES &
  \textbf{Solution Concentration:}5$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} Dual-28G-needle array with needle inner diameter of 0.18$mm $ and outer diameter of 0.36$mm $; with needle spacing changes from 2.0$mm $ to 3.0$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 0.2$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 3.0-4.0$mm $ \mbox{}\protect\newline \textbf{Substrate composition: }\textit{Not determined} \mbox{}\protect\newline \textbf{Applied voltage:} 2.0-3.0$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 218-326$\mu m $ &
  \unskip~\cite{527120:11974323}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
  Multinozzle NFES &
  \textbf{Solution Concentration:}5 $wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} Dual-28G-needle array with needle inner diameter of 180$\mu m $ and outer diameter of 360$\mu m $; with needle spacing changes of 2.0$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 0.2$\mu L / min $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 4.0$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} chromium-plated glass \mbox{}\protect\newline \textbf{Applied voltage:} 2.5$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 20$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 2.3002-2.7224$mm $ &
  \unskip~\cite{527120:11974324}\\\cline{1-1}\cline{2-2}\cline{3-3}\cline{4-4}\cline{5-5}
  Typical NFES process &
  \textbf{Solution Concentration:} 2$wt\% $ \mbox{}\protect\newline \textbf{Nozzle:} G30 needle with inner diameter of 0.15$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:}\textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1-3$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Silicon \mbox{}\protect\newline \textbf{Applied voltage:} 1250$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} \textit{Not determined} \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 20$\mu m $ &
  \unskip~\cite{527120:11974325}\\
Gelatin \mbox{}\protect\newline (porcine skin) &
  Acetic Acid and Ethyl Acetate &
  Typical NFES process &
  \textbf{Solution Concentration:} 11$wt\% $ gelatin, 30$wt\% $ water, 35.4$wt\% $ acetic acid, 23.6$wt\% $ ethyl acetate \mbox{}\protect\newline \textbf{Nozzle:} 19G needle tip with outer diameter of 1.08$mm $ \mbox{}\protect\newline \textbf{Solution deposition rate:}\textit{Not determined} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1.25$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Poly(Dimethylsiloxane) (PDMS) films \mbox{}\protect\newline \textbf{Applied voltage:} 1000$V $ \mbox{}\protect\newline \textbf{x-y stage velocity:} \textit{Not determined} \mbox{}\protect\newline \textbf{Fiber Diameter:} around 2-3$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 40$\mu m $ &
  \unskip~\cite{527120:11974326}\\
  Water/Ethanol (v/v = 60/40) &
  Typical NFES process &
  \textbf{Solution Concentration:} PEO concentrations of 16\% adn 18\% \mbox{}\protect\newline \textbf{Nozzle:} 40$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 1$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Planar silicon \mbox{}\protect\newline \textbf{Applied voltage:} 1.7$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 0.36$m/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 5.15$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} \textit{Not determined} &
  \unskip~\cite{527120:11974327}\\
  Water/Ethanol (v/v = 3/1) &
  Electrohydro-dynamic Direct-Write (EDW) &
  \textbf{Solution Concentration:} 14$wt\% $ PEO \mbox{}\protect\newline \textbf{Nozzle:} Stainless needle with inner diameter of 210$\mu m $ and outer diameter of 400$\mu m $ \mbox{}\protect\newline \textbf{Solution deposition rate:} 50$\mu L/h $ \mbox{}\protect\newline \textbf{Nozzle-to-substrate distance:} 2$mm $ \mbox{}\protect\newline \textbf{Substrate composition:} Poly(ethylene terephthalate) (PET) \mbox{}\protect\newline \textbf{Applied voltage:} 3$kV $ \mbox{}\protect\newline \textbf{x-y stage velocity:} 700$mm/s $ \mbox{}\protect\newline \textbf{Fiber Diameter:} 15-35$\mu m $ \mbox{}\protect\newline \textbf{Distance between adjacent fibers:} 70$\mu m $ &
  \unskip~\cite{527120:11974328}\\

@@

\textbf{Solution Concentration:}

\textbf{Nozzle:}

\textbf{Solution deposition rate:}

\textbf{Nozzle-to-substrate distance:}

\textbf{Substrate composition:}

\textbf{Applied voltage:}

\textbf{x-y stage velocity:}

\textbf{Fiber Diameter:}

\textbf{Distance between adjacent fibers:}
